Cleaning Data

### 2021-07-28 cleaning_aid.Rmd
codes for 'app used'
Gene set version cleaned
gene set version cleaned
fix name change

x <- read.table("PMC 2019 - analysis.tsv",header=TRUE,fill=TRUE,sep="\t")
head(x)
colnames(x)
dim(x)

@@

>>>>

x <- read.table("PMC_2019-analysis.tsv",header=TRUE,fill=TRUE,sep="\t")
head(x)
colnames(x)
dim(x)

@@

# App used
App <-x$App.used
App_split <- strsplit(App,", ")
App <- unlist(App_split)
table(App)

# Gene set version
GSV <-x$GS.version
table(GSV)
